Morphology-based Entity and Relational Entity Extraction Framework for Arabic

### 2018-06-27 tex/merf/TALMajor/abstract.tex
french translation and shrink first page

Rule-based techniques and tools to extract entities and relational entities from documents allow users to specify desired entities using natural language questions, finite state automata, regular expressions, structured query language statements, or proprietary scripts.
These techniques and tools require expertise in linguistics and programming.
They lack support of Arabic morphological analysis which is key to 
process Arabic text.
In this work, we present \framework; a morphology-based entity and relational entity extraction framework for Arabic text.
\framework provides a friendly interface where the user, with basic knowledge of linguistic features and regular expressions, defines tag types and interactively associates them with regular expressions defined over Boolean formulae.
Boolean formulae range over matches of Arabic morphological features, and synonymity features.
Users define relations with tuples of subexpression matches and can associate code actions with subexpressions.
\framework computes feature matches, regular expression matches, and constructs entities and relational entities from the user-defined relations.
We evaluated our work with several case studies and compared with existing application-specific techniques.
The results show that \framework requires shorter development time and effort compared to existing techniques and produces reasonably accurate results within a reasonable overhead in run time.

>>>>

Rule-based techniques to extract relational entities from 
documents allow users to specify desired entities with 
natural language questions, finite state automata, regular expressions and
structured query language. 
They require linguistic and programming expertise and 
lack support for Arabic morphological analysis.
We present a morphology-based entity and relational entity extraction 
framework for Arabic (\framework).
\framework requires
basic knowledge of linguistic features and regular expressions, 
and provides the ability to interactively specify
Arabic morphological and synonymity features, 
tag types associated with regular expressions, and
relations and code actions defined over matches of subexpressions. 
\framework constructs entities and relational entities from matches 
of the specifications.
We evaluated \framework with several case studies.
The results show that \framework requires shorter development time and effort compared to existing application specific techniques and produces 
reasonably accurate results within a reasonable overhead in run time.

### 2018-06-27 tex/merf/TALMajor/macros.tex
minor changes
french translation and shrink first page

%%%%%%%% packages %%%%%%%%%%
\usepackage{xspace}
\usepackage{arabtex}
\usepackage{array}
\usepackage{tikz}
\usepackage{hyperref}
\hypersetup{
    colorlinks=false,
    pdfborder={0 0 0},
}
\usepackage{booktabs}
\usepackage[ruled]{algorithm2e}
\usepackage{etex}
\usepackage{graphicx}
\usepackage{framed}
\usepackage{graphics}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{savesym}
\savesymbol{bigtimes}
\usepackage{mathabx}
\restoresymbol{TXF}{bigtimes}
\usepackage{utf8}
\usepackage{subfigure}
\usepackage{todonotes}
\usetikzlibrary{shapes,arrows}
\usepackage{color,soul}
\usepackage{verbatim}
\usepackage{array}
\usepackage{multicol}
\usepackage{fancyvrb}
\usepackage{relsize}
\usepackage{wasysym}
\usepackage{pbox}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%% Macros %%%%%%%%%%
\def\framework{\textsc{MERF}\xspace}
\newcommand{\itodo}[1]{\todo[inline,color=green]{\tiny #1}}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcommand{\TinyRL}[1]{{\RL{#1}}}
\newcommand{\cci}[1]{{\small \texttt{#1}}}
%%% RL commands
\newcommand{\utfrl}[1]{\setcode{utf8}\RL{#1}\setcode{standard}}
\newcommand{\notrutfrl}[1]{\transfalse\setcode{utf8}\RL{#1}\setcode{standard}\transtrue}
\newcommand{\notrrl}[1]{\transfalse\RL{#1}\transtrue}
\newcommand{\noarrl}[1]{\arabfalse\RL{#1}\arabtrue}
\def\showvrb#1{%
\texttt{\detokenize{#1}}%
}
%%% define cal
\makeatletter
\DeclareRobustCommand*\cal{\@fontswitch\relax\mathcal}
\makeatother
% done
%other 
% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\title[\framework]{\framework: Morphology-based Entity and Relational Entity Extraction Framework for Arabic}

@@

\author{}
%\author{Amin A. Jaber \andauthor Fadi A. Zaraket}

\address{}
%\address{American University of Beirut, Beirut 1107 2020, Lebanon}

@@

\keywords{
Arabic,
information extraction,
natural language processing,
entity,
relational entity,
information visualization,
tagging.
}

\motscles{
%mot-cl\'e$_1$,
%mot-cl\'e$_2$,
%mot-cl\'e$_3$.
}

\resume{
%Le r\'esum\'e est \`a \'ecrire ici.
}

>>>>

%%%%%%%%% packages %%%%%%%%%%
\usepackage{xspace}
\usepackage{arabtex}
\usepackage{array}
\usepackage{tikz}
\usepackage{url}
%\usepackage{hyperref}
%\hypersetup{
%    colorlinks=false,
%    pdfborder={0 0 0},
%}
%\usepackage{booktabs}
%\usepackage[ruled]{algorithm2e}
%\usepackage{etex}
%\usepackage{graphicx}
%\usepackage{framed}
%\usepackage{graphics}
\usepackage{booktabs}
\usepackage{multirow}
%\usepackage{amssymb}
%\usepackage{amsmath}
%\usepackage{savesym}
%\savesymbol{bigtimes}
\usepackage{mathabx}
%\restoresymbol{TXF}{bigtimes}
\usepackage{utf8}
%\usepackage{subfigure}
%\usetikzlibrary{shapes,arrows}
%\usepackage{color,soul}
\usepackage{verbatim}
%\usepackage{multicol}
\usepackage{fancyvrb}
\usepackage{relsize}
\usepackage{wasysym}
%\usepackage{pbox}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%%%%%%%%%%% Macros %%%%%%%%%%
%\newcommand{\major}[1]{{\color{black}#1}}
\def\framework{\textsc{MERF}\xspace}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcommand{\TinyRL}[1]{{\RL{#1}}}
\newcommand{\cci}[1]{{\small \texttt{#1}}}
%%% RL commands
\newcommand{\utfrl}[1]{\setcode{utf8}\RL{#1}\setcode{standard}}
\newcommand{\notrutfrl}[1]{\transfalse\setcode{utf8}\RL{#1}\setcode{standard}\transtrue}
\newcommand{\notrrl}[1]{\transfalse\RL{#1}\transtrue}
\newcommand{\noarrl}[1]{\arabfalse\RL{#1}\arabtrue}
%\def\showvrb#1{%
%\texttt{\detokenize{#1}}%
%}
%%% define cal
%\makeatletter
%\DeclareRobustCommand*\cal{\@fontswitch\relax\mathcal}
%\makeatother
% done
%other 
% correct bad hyphenation here
%\hyphenation{op-tical net-works semi-conduc-tor}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\title[\framework]{Morphology-based Entity and Relational Entity Extraction Framework for Arabic}

@@

\author{Amin Jaber \andauthor Fadi A. Zaraket}

\address{American University of Beirut, Beirut 1107 2020, Lebanon}

@@

\keywords{
Arabic,
information extraction,
natural language processing,
tagging.
}

\motscles{
Arabe,
extraction d'information,
traitement du langage naturel,
marquage.
}

\resume{
Les techniques à base de règles pour extraire des entités permettent 
de spécifier les entités souhaitées en utilisant des questions 
de langage naturel, des automates à états finis, des expressions régulières, et des 
instructions d'extraction de données.
Ils nécessitent des expertises en linguistique et en programmation et
ne soutiennent pas l'analyse morphologique d'Arabe.
On présente pour l'Arabe 
un cadre d'extraction d'entité 
renforcé par l'analyse morphologique (\framework). 
Il exige des connaissances be base des 
caractéristiques linguistiques et des expressions régulières, 
et fournit la pouvoire de spécifier de façon interactive 
des fonctionnalités de morphologie et synonymie Arabe,
des types de tag associés avec des expressions régulières, 
et des relations et actions de code définies sur les correspondances de sous-expressions.
\framework construit des entités relationnelles à partir des correspondances
des spécifications.
On évalue \framework avec des études de cas.
Les résultats montrent que \framework nécessite un effort de développement plus courts par rapport aux techniques existantes 
et produit des résultats raisonnablement précis avec une surcharge raisonnable en temps d'exécution.
}
